### 2016-06-29 testbed.tex
.

The testbed consists of up to one hundred \ac{Raspi}s of different models.
More specifically, Raspberry Pi 1 model B rev.~2,
Raspberry Pi 2 model B V1.1, and Raspberry Pi 3 model B V1.2.
All \ac{Raspi}s are each equipped with a memory card, a wired, and a wireless
network interface. They connect to the university network using its wired
ethernet interface that is named \texttt{eth0} according to the legacy naming
convention of ethernet interfaces in Linux. \textcolor{red}{MAYBE PUT SOUECE HERE}

@@

A sketch of the testbed is depicted in Figure~\ref{fig:testbed_setup}.

@@

The following procedure will explain how the testbed may be setup and
configured both in the traditional distributed fasion where the
entire Linux filesystem is written to an memory card, but also in a more
centralized fasion where 
is written to
Based on the popular Debian based Raspbian Linux distribution
We
first present how a standard Linux distribution for the \ac{Raspi}s
may be customized

>>>>

The testbed consists of up to one hundred \ac{Raspi}s of different models.
More specifically, Raspberry Pi 1 model B rev.~2,
Raspberry Pi 2 model B V1.1, and Raspberry Pi 3 model B V1.2.
All \ac{Raspi}s are each equipped with a memory card, a wired, and a wireless
network interface. They connect to the university network using its wired
ethernet interface that is named \texttt{eth0} according to the legacy naming
convention of ethernet interfaces in Linux~\cite{PredictableNetworkInterfaceNames}.

@@

A sketch of the testbed is depicted in Figure~\ref{fig:testbed_setup}.
The testbed is intended for students to perform simulations and measurements
as part of semester projects. We therefore intend to configure all
\ac{Raspi}s identically, while still allowing students to alter how each
\ac{Raspi} behaves and is configured.

The following produre explains a way to setup the testbed to facilitates these
requirements. The procedure is assumed to be performed by whom we will refer
to as the testbed administrator in a \ac{PC} running Linux. The exact Linux
distribution is does not matter, but the procedure will be based on
Debian Linux.

@@

The following procedure explains how the testbed may be setup and configured.

%The following procedure will explain how the testbed may be setup and
%configured both in the traditional distributed fasion where the
%entire Linux filesystem is written to an memory card, but also in a more
%centralized fasion where 
%is written to
%Based on the popular Debian based Raspbian Linux distribution
%We
%first present how a standard Linux distribution for the \ac{Raspi}s
%may be customized
